\begin{thebibliography}{99}
	\bibitem{Cirac_1995} J. I. Cirac and P. Zoller, \textit{Quantum Computations with Cold Trapped Ions}, Phys. Rev. Lett. \textbf{74}, 4091 (1995)
	\bibitem{Wright_2019}  Wright, K., Beck, K. M., Debnath, S. \textit{et al.}, \textit{Benchmarking an 11-qubit quantum computer}, Nat. Commun. \textbf{10}, 5464 (2019)
	\bibitem{Cirac_2000} Cirac, J. and Zoller, P., \textit{A scalable quantum computer with ions in an array of microtraps}, Nature \textbf{404}, 579–581 (2000). 
	\bibitem{Mielenz_2016} Mielenz, M., Kalis, H., Wittemer, M. \textit{et al.}, \textit{Arrays of individually controlled ions suitable for two-dimensional quantum simulations}, Nat. Commun. \textbf{7}, ncomms11839 (2016)
	\bibitem{Narayanan_2011} S. Narayanan, N. Daniilidis, S. A. Möller, R. Clark, F. Ziesel, K. Singer, F. Schmidt-Kaler, and H. Häffner , \textit{Electric field compensation and sensing with a single ion in a planar trap}, J. Appl. Phys. \textbf{110}, 114909 (2011)
	\bibitem{Danii_2014} N. Daniilidis, S. Gerber, G. Bolloten, M. Ramm, A. Ransford, E. Ulin-Avila, I. Talukdar, and H. Häffner, \textit{Surface noise analysis using a single-ion sensor}, Phys. Rev. B \textbf{89}, 245435
	\bibitem{Berkeland_1998} D. J. Berkeland, J. D. Miller, J. C. Bergquist, W. M. Itano, and D. J. Wineland , \textit{Minimization of ion micromotion in a Paul trap}, J. Appl. Phys \textbf{83}, 5025-5033 (1998)
	\bibitem{Chen_2020} Chen, T., Wu, W., Xie, Y. \textit{et al.}, \textit{Controlling the rf phase error induced micromotion in Paul trap}, Appl. Phys. B \textbf{126}, 102 (2020)
	\bibitem{Timm_2015} Timm F. Gloger, Peter Kaufmann, Delia Kaufmann, M. Tanveer Baig, Thomas Collath, Michael Johanning, and Christof Wunderlich, \textit{Ion-trajectory analysis for micromotion minimization and the measurement of small forces}, Phys. Rev. A \textbf{92}, 043421
	\bibitem{Tanaka_2021} U. Tanaka, M. Nakamura, K. Hayasaka, A. Bautista-Salvadora, C.Ospelkaus, and T. E. Mehlstäubler, \textit{Creation of double-well potentials in a surface-electrode trap towards a nanofriction model emulator}, Quantum Sci. Technol. \textbf{6} 024010(2021)
	\bibitem{L-Timm_2021} L. Timm, L. A. Rüffert, H. Weimer, L. Santos, and T. E. Mehlstäubler, \textit{Quantum nanofriction in trapped ion chains with a topological defect}, Phys. Rev. Research \textbf{3}, 043141(2021)
	\bibitem{URABE} 占部伸二, "個別量子系の物理 イオントラップと量子情報処理", 朝倉書店 (2017)
	\bibitem{Kielpinski_2002} Kielpinski, D., Monroe, C. and Wineland, D., \textit{Architecture for a large-scale ion-trap quantum computer}, Nature \textbf{417}, 709–711 (2002)
	\bibitem{House_2008} M. G. House, \textit{Analytic model for electrostatic fields in surface-electrode ion traps}, Phys. Rev. A \textbf{78}, 033402(2008)
	\bibitem{Wineland_1979} D. J. Wineland and W. D. Itano, \textit{Laser cooling of atoms}, Phys. Rev. A \textbf{20}, 1521
	\bibitem{Lechner_2016} Regina Lechner, Christine Maier, Cornelius Hempel, Petar Jurcevic, Ben P. Lanyon, Thomas Monz, Michael Brownnutt, Rainer Blatt, and Christian F. Roos, \textit{Electromagnetically-induced-transparency ground-state cooling of long ion strings}, Phys. Rev. A \textbf{93}, 053401(2016)
	\bibitem{Brownnutt_2012} Brownnutt, M., Harlander, M., Hänsel, W. \textit{et al.}, \textit{Spatially-resolved potential measurement with ion crystals}, Appl. Phys. B \textbf{107}, 1125–1130 (2012).
	\bibitem{NIST} https://physics.nist.gov/PhysRefData/ASD/lines\_form.html
	\bibitem{Welzel_2011} J. Welzel, A. Bautista-Salvador, C. Abarbanel, V. Wineman-Fisher, C. Wunderlich, R. Folman, and F. Schmidt-Kaler, \textit{Designing spin-spin interactions with one and two dimensional ion crystals in planar micro traps}, Eur. Phys. J. D \textbf{65}, 285-297 (2011)
\end{thebibliography}
